Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-20 minimax.tex
new xps

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=10}
%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
%			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
			\addlegendentry{tshirts m11n30}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
			\addlegendentry{courses m9n146}
			%\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/m14n9.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}

>>>>

			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {35}, teal] table [x=k, y=5.10]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=10}
%			\addplot[thick, mark=*, mark size = {2}, mark indices = {45}, violet] table [x=k, y=5.15]{data/normalizedLin.dat};
%			\addlegendentry{m=5, n=15}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {90}, green] table [x=k, y=5.20]{data/normalizedLin.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {300}, cyan] table [x=k, y=10.30]{data/normalizedLin.dat};
			\addlegendentry{m=10, n=30}
			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirt]{data/normalizedLin.dat};
			\addlegendentry{tshirts m11n30}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/normalizedLin.dat};
			\addlegendentry{courses m9n146}
			%\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/normalizedLin.dat};
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/m14n9.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, brown] table [x=k, y=skate]{data/normalizedLin.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/normalizedLin.dat};
			\addlegendentry{m=15, n=30}

			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, orange] table [x=k, y=14.10]{data/new.dat};
			\addlegendentry{m=14, n=10}
			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {60}, black] table [x=k, y=15.10]{data/new.dat};
			\addlegendentry{m=15, n=10}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, yellow] table [x=k, y=15.9]{data/new.dat};
			\addlegendentry{m=15, n=9}
		\end{axis}
	\end{tikzpicture}
\end{figure}

%\begin{table}
%	\caption{Average number of questions asked to the chair (\textit{qstC}) and to the agents (\textit{qstV}) by Pessimistic strategy to reach zero regret on the data sets of \cref{fig:linearity}.}
%	\label{tab:questions}
%	\begin{tabular}{S[table-text-alignment=right] S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
%		\toprule
%		{data set} & {qstC} & {sd} & {qstV} & {sd} \\
%		\midrule
%		m5n10 &		8.4		& 2.67 		& 61		& 6.25\\
%		m5n20 &		13.6	& 6.38		& 118.9		& 14.4\\
%		m10n20 &	48.5	 & 6		& 362.4		& 47.6	\\
%		m10n30 &	56.3	&	11.18	&598.1 		&75.19	\\
%		m15n30 &	24.5	&8.77		&	775.5	&	8.77	\\
%		m14n9 &		58.3	&33.66		&370.9		&40.54	\\
%		m14n9-2 &	56.2	&34.11		&368.7		&	53.07 \\
%		skate &	0		& 0			&103.3		&2.21	\\
%		tshirt &	30.0	&	15.87	&	961.2	&	23.04	\\
%		courses & 0		& 0		&950		&5.08	\\
%		
%		\bottomrule
%	\end{tabular}
%\end{table}
